---
output:
  word_document:
    reference_docx: style.docx
always_allow_html: true
---


```{r,echo=FALSE,cache=TRUE,include=FALSE}

library(magrittr)
library(estimatr)
library(tidyverse)
library(flextable)
library(officer)
###library(directlabels)
library(ggrepel)
library(knitr)
library(rmarkdown)
select <- dplyr::select
source('R/trends.r')

load('output/estByYear.RData')
load('output/ageDist18.RData')

overTimeAge <- processEsts(overTimeAge,ageDist18)

overTime <- processEsts(overTime)

### estimate trends

subs <- c('Tot',
          'ByAgeCat',
          'Sex','Race','RaceM','RaceF')%>%
  setNames(.,.)

tables <- allTabs(overTimeAge, overTime,onlyDeaf=TRUE,digits=1)

printTab <- function(tab)#,level)
    tab%>%
    flextable()%>%
    set_header_labels(SUB='Grouping',subgroup='Subgroup')%>%
    border_remove()%>%
    merge_v(j='SUB')%>%
    hline_bottom(part='header',border=fp_border(width=2))%>%
    hline(i=c(2,4,10,16),border=fp_border())%>%
    add_header_row(top=TRUE ,c("","Rates\n(%)","Trends\n(Percentage Points/Year)"),colwidths=c(2,2,2))%>%
    align(align='center',part='header')%>%
    align(j=1:2,align='right',part='all')%>%
    align(j=3:6,align='left',part='body')%>%
    #fontsize(size=12,part='header')%>%
      #add_footer_lines(paste("_note:_ Rates and trends refer to the percentage of people who have attained at least a",level,"Degree. Standard errors are in parentheses. All results were computed from the ACS PUMS single year data, with person weights. Standard errors for attainment rates were computed with the successive difference replication method using the person replication weights provided with the PUMS. Standard errors for trends are HC2 standard errors from the regressions described in the text."))%>%
    #merge_at(j=1:6,part='footer')%>%
    ## add_footer(SUB="*p < .05. **p < .01. ***p < .001 (corrected for multiplicity)")%>%
    ## merge_at(i=2,j=1:6,part='footer')%>%
    autofit(add_w=0)%>%
    #padding(padding=0,part='all')%>%
    #fit_to_width(8.5)%>%
    height(height=.5,part='header')

```
```{r makeFigures, include=FALSE,cache=TRUE}
for(lev in c('hs','cc','bach')){
    figFun(lev,overTime)
    ggsave(paste0('figures/',lev,'.png'),width=6.4,height=6)
}
```

\newline



**Table 1**

\newline

_Deaf High School Completion from 2008 to 2018_
```{r hs, results='asis',warning=FALSE,message=FALSE,error=FALSE,echo=FALSE,cache=FALSE}
printTab(tables$hs)
```
_Note:_ Rates and trends refer to the percentage of people who have
attained at least a high school degree. Standard errors are in
parentheses. All results were computed from the ACS PUMS single year
data, with person weights. Standard errors for attainment rates were
computed with the successive difference replication method using the
person replication weights provided with the PUMS. Standard errors for
trends are HC2 standard errors from the regressions described in the
text.

*p < .05. \*\*p < .01. \*\*\*p < .001 (corrected for multiplicity)

##### page break

**Table 2**

\newline

_Deaf Associate Degree Attainment from 2008 to 2018_
```{r cc, results='asis',warning=FALSE,message=FALSE,error=FALSE,echo=FALSE,cache=FALSE}
printTab(tables$cc)

```

##### page break

**Table 3**

\newline

_Deaf Bachelors' Completion from 2008 to 2018_
```{r ba, results='asis',warning=FALSE,message=FALSE,error=FALSE,echo=FALSE,cache=FALSE}
printTab(tables$bach)

```

